SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/poly.tex
Add citations from reviewer comments in PR 100.

At the lowest level of the new design are classes which represent univariate
piecewise polynomials: \code{PPoly}, \code{BPoly} and \code{BSpline}, which allow
efficient vectorized evaluations, differentiation, integration and root-finding.
\code{PPoly} represents piecewise polynomials in the power basis in terms of
breakpoints and coefficients at each interval. \code{BPoly} is similar, and
represents piecewise polynomials in the Bernstein basis (which is suitable
for e.g., constructing Bezier curves). \code{BSpline} represents spline
curves, i.e., linear combinations of b-spline basis elements.\cite{deBoor1978}.

In the next layer, these polynomial classes are used for constructing several
common ways of interpolating data: \code{CubicSpline} constructs a twice 
differentiable piecewise cubic function, \code{Akima1DInterpolator} 
and \code{PCHIPInterpolator} implement two classic prescriptions for
constructing a $C^1$ continuous monotone shape-preserving interpolator.
\cite{FritschCarlson1980, Akima1970}

>>>>

At the lowest level of the new design are classes which represent univariate
piecewise polynomials: \code{PPoly} (SciPy 0.13)\cite{scipy-gh5827},
\code{BPoly} (SciPy 0.13) and \code{BSpline} (SciPy 0.19)\cite{scipy-gh3174},
which allow
efficient vectorized evaluations, differentiation, integration and root-finding.
\code{PPoly} represents piecewise polynomials in the power basis in terms of
breakpoints and coefficients at each interval. \code{BPoly} is similar, and
represents piecewise polynomials in the Bernstein basis (which is suitable
for e.g., constructing Bezier curves). \code{BSpline} represents spline
curves, i.e., linear combinations of b-spline basis elements.\cite{deBoor1978}

In the next layer, these polynomial classes are used for constructing several
common ways of interpolating data: \code{CubicSpline} (SciPy 0.18)
\cite{scipy-gh5653} constructs a twice 
differentiable piecewise cubic function, \code{Akima1DInterpolator} 
and \code{PCHIPInterpolator} implement two classic prescriptions for
constructing a $C^1$ continuous monotone shape-preserving interpolator.
\cite{FritschCarlson1980, Akima1970}
